### 2014-07-23 MS.tex
sup inf legends

\textbf{\texttt{supp\_mat\_01\_genus.nex}}: MCC Nymphalidae tree from
Reference 10.

\textbf{\texttt{supp\_mat\_02\_run\_medusa\_on\_mct.R}}: Run MEDUSA on
MCC tree from Reference 10.

\textbf{\texttt{supp\_mat\_03\_richness.nex}}: Species richness for
lineages in Nymphalidae.

\textbf{\texttt{supp\_mat\_04\_MEDUSA\_results.txt}}: Results of running
MEDUSA on the MCC tree.

\textbf{\texttt{supp\_mat\_05\_1000\_random\_trees\_no\_outgroups.nex}}:
1000 random trees from Reference 10.

\textbf{\texttt{supp\_mat\_06\_run\_multimedusa.R}}: Run MultiMEDUSA on
1000 random trees from Reference 10.

\textbf{\texttt{supp\_mat\_07\_multimedusa\_on\_1000\_trees.txt}}: Raw
results from the MultiMEDUSA run on the random sample of trees from the
posterior distribution.

\textbf{\texttt{supp\_mat\_08\_multimedusa\_result01.pdf}}: Summary of
MulitMEDUSA analysis on the 1000 trees from the posterior distribution.

\textbf{\texttt{supp\_mat\_09\_mcc\_tree\_from\_random\_sample\_of\_1000.tree}}:
MCC tree from the 1000 random trees selected from the posterior
distribution.

\textbf{\texttt{supp\_mat\_10\_run\_medusa\_on\_mct\_from\_1000\_trees.R}}:
Run MEDUSA on MCC tree from the 1000 random trees selected from the
posterior distribution.

\textbf{\texttt{supp\_mat\_11\_results\_of\_MEDUSA\_run\_on\_mcc\_from\_1000\_trees.txt}}:
Summary results from a MEDUSA run on the MCC tree from the 1000 random
trees selected from the posterior distribution.

\textbf{\texttt{supp\_mat\_12\_MEDUSA\_mcc\_tree\_from\_random\_sample\_of\_1000\_trees.pdf}}:
Figure for MEDUSA run on MCC tree from random 1000 trees.

\textbf{\texttt{supp\_mat\_13\_results\_of\_Multi-MEDUSA\_run\_on\_1000\_trees.txt}}:
Summary results from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution.

\textbf{\texttt{supp\_mat\_14\_multimedusa\_result\_prob\_nodes.pdf}}:
Probability of nodes with estimated rates from a MultiMEDUSA run on the
1000 random trees selected from the posterior distribution.

\textbf{\texttt{supp\_mat\_15\_host\_plant\_data.csv}}: Hostplants of
Nymphalidae butterflies recorded from the literature.

\textbf{\texttt{supp\_mat\_16\_host\_plant\_data\_references.csv}}:
References for hostplants data.

\textbf{\texttt{supp\_mat\_17\_hostplant\_states.csv}}: Data matrix with
character states for hosplant use.

\textbf{\texttt{supp\_mat\_18\_bisse\_source.R}}: R code for running the
BiSSE analysis.

\textbf{\texttt{supp\_mat\_19\_bisse\_mcmc\_run.csv}}: Raw results for
the BiSSE analysis.

\textbf{\texttt{supp\_mat\_20\_combined\_bisse.csv}}: Raw results for
the combined BiSSE analysis.

\texttt{Figure S1.} Boxplot of speciation (lambda) and extinction (mu)
values for the 95\% credibility intervals of values estimated by BiSSE
analysis of diversification due to feeding on Solanaceae plants.

\texttt{Figure S2.} BiSSE analysis of diversification of nymphalids due
to feeding on Solanaceae hostplants assuming \emph{Vanessa} and
\emph{Hypanartia} as non-Solanaceae feeders. The same pattern is
recovered, speciation and net diversification rates are significantly
higher for Solanaceae feeders (\$lambda\$1, r1).

\texttt{Figure S3.} Net diversification rates of nymphalids feeding on
Solanaceae plants as estimated by combining post-burnin runs of BiSSE on
the 1000 trees from the posterior distribution.

\texttt{Figure S4.} Boxplot of speciation and extinction values for the
95\% credibility intervals of values estimated by BiSSE analysis of
diversification due to feeding on Solanaceae plants on the combined
post-burnin runs on 1000 trees from the posterior distribution.

\texttt{Figure S5.} BiSSE analysis of diversification of nymphalids due
to feeding on Apocynaceae hostplants. Speciation and net diversification
rates are similar.

@@

>>>>

@@

\textbf{\texttt{Supporting_Information_S1.nex}}: \textbf{Genus}. MCC Nymphalidae tree from
Reference 10.

\textbf{\texttt{Supporting_Information_S2.R}}: \textbf{Run_medusa_on_mct}. Run MEDUSA on
MCC tree from Reference 10.

\textbf{\texttt{Supporting\_Information\_S3.csv}}: Species richness for
lineages in Nymphalidae.

\textbf{\texttt{Supporting\_Information\_S4.txt}}: Results of running
MEDUSA on the MCC tree.

\textbf{\texttt{Supporting\_Information\_S5.zip}}: 1000 random trees from Reference 10.

\textbf{\texttt{Supporting\_Information\_S6.R}}: Run MultiMEDUSA on
1000 random trees from Reference 10.

\textbf{\texttt{Supporting\_Information\_S7.zip}}: Raw
results from the MultiMEDUSA run on the random sample of trees from the
posterior distribution.

\textbf{\texttt{Supporting\_Information\_S8.pdf}}: Summary of
MulitMEDUSA analysis on the 1000 trees from the posterior distribution.

\textbf{\texttt{Supporting\_Information\_S9.tree}}:
MCC tree from the 1000 random trees selected from the posterior
distribution.

\textbf{\texttt{Supporting_Information_S10.R}}:
Run MEDUSA on MCC tree from the 1000 random trees selected from the
posterior distribution.

\textbf{\texttt{Supporting_Information_S11.txt}}:
Summary results from a MEDUSA run on the MCC tree from the 1000 random
trees selected from the posterior distribution.

\textbf{\texttt{Supporting_Information_S12.pdf}}:
Figure for MEDUSA run on MCC tree from random 1000 trees.

\textbf{\texttt{Supporting_Information_S13.txt}}:
Summary results from a MultiMEDUSA run on the 1000 random trees selected
from the posterior distribution.

\textbf{\texttt{Supporting_Information_S14.pdf}}:
Probability of nodes with estimated rates from a MultiMEDUSA run on the
1000 random trees selected from the posterior distribution.

\textbf{\texttt{Supporting_Information_S15.csv}}: Hostplants of
Nymphalidae butterflies recorded from the literature.

\textbf{\texttt{Supporting_Information_S16.csv}}:
References for hostplants data.

\textbf{\texttt{Supporting_Information_S17.csv}}: Data matrix with
character states for hosplant use.

\textbf{\texttt{Supporting_Information_S18.R}}: R code for running the
BiSSE analysis.

\textbf{\texttt{Supporting_Information_S19.csv}}: Raw results for
the BiSSE analysis.

\textbf{\texttt{Supporting_Information_S20.csv}}: Raw results for
the combined BiSSE analysis.
